Talks

### 2025-09-09 talks.qmd
update

@@

>>>>

- 6th October: [ARMA Research Evaluation SIG Drop-In Session: Randomisation in funding allocation](https://arma.ac.uk/product/arma-research-evaluation-sig-drop-in-session-randomisation-in-funding-allocation/)

@@

- [The Metascience Lab](https://docs.google.com/presentation/d/1hcrkLVRyFl2zAhXffWldhXhNFYqkRLJj/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true), days 1, 2 & 3 at Metascience 2025, June 30 - 2 July, London.
